Can Zero-shot LLMs save additional work in machine learning prioritised screening for systematic reviews?

### 2024-11-04 LLMs/manuscript/main.tex
Updates from Overleaf

	\begin{abstract}
		Zero shot learning using LLMs has received widespread attention in recent years, including in the automation of systematic review screening. 
		However, there has been insufficient research on robust processes to automate screening responsibly. 
		For systematic review screening, responsible automation requires that the risks of missing relevant studies (which are inherent when the process is automated) can be accurately quantified and managed.
		In this paper, we adapt LLM-assisted screening to the widespread machine learning prioritised screening paradigm, and use robust stopping criteria to quantify how much work can be responsibly saved with different levels of risk tolerance for missing studies.
		We find that that - even in the absence of detailed inclusion and exclusion criteria - LLM-assisted screening can save on average [x] percentage points of additional work compared to a baseline model.
		Across the whole database of [x] systematic review datasets, which would have required [x] hours to screen manually, LLM-assisted screening can reduce the time required to [x] hours, with the next best model reducing the time required to [y] hours, while still ensuring a 95\% chance of missing no more than 5\% of relevant studies.
	\end{abstract}

@@

	However, the paper proposes a strategy to save work using the model that is not able to accurately quantify or mitigate the risk of missing studies. Documents with an inclusion score greater than a threshold paramater $\theta$ are screened by hand, while all remaining documents are automatically excluded. The methods proposed to set the threshold paramater (either extrapolating from other reviews, or by setting the paramater such that it achieves the desired recall level on a set of predefined relevant documents) are \textit{not} able to reliably ensure that a desired level of recall is met.

@@

@@

	\bibliography{../stopping-criteria}
	%\bibliography{../LLMs}

>>>>

	\begin{abstract}
		Zero shot learning using LLMs has received widespread attention in recent years, including in the automation of systematic review screening. 
		However, there has been insufficient research on robust processes to automate screening responsibly. 
		For systematic review screening, responsible automation requires that the risks of missing relevant studies (which are inherent when the process is automated) can be accurately quantified and managed.
		In this paper, we adapt LLM-assisted screening to the widespread machine learning prioritised screening paradigm, and use robust stopping criteria to quantify how much work can be responsibly saved with different levels of risk tolerance for missing studies.
		We find that - even in the absence of detailed inclusion and exclusion criteria - LLM-assisted screening can produce ranked lists of documents that are superior to those generated by the baseline.
		However, LLMs do not seem to be a silver bullet which would substantially reduce the amount of work required to complete screening. Across a variety of recall targets and confidence levels, work savings were generally higher with the SVM baseline, though possible work savings with LLMS were higher in low recall or low confidence settings. 
	\end{abstract}

@@

	However, the paper proposes a strategy to save work using the model that is not able to accurately quantify or mitigate the risk of missing studies. Documents with an inclusion score greater than a threshold parameter $\theta$ are screened by hand, while all remaining documents are automatically excluded. The methods proposed to set the threshold parameter (either extrapolating from other reviews, or by setting the parameter such that it achieves the desired recall level on a set of predefined relevant documents) are \textit{not} able to reliably ensure that a desired level of recall is met.

@@

    Similarly, a paper by Xia and co-authors \cite{xia_llmscreen_2024} highlights the lack of commonly agreed upon stopping criteria as a limitation of current approaches to ml-assisted screening, and proposes LLM-based screening as a solution.

@@

	\bibliography{LLMs/stopping-criteria}
	%\bibliography{../LLMs}
